Learning CNN filters from user-drawn image makers for coconut-tree image classification

### 2020-06-08 main.tex
Updates from Overleaf

Classification of tree species in aerial images has been actively investigated~\cite{fassnacht2016review}. In \cite{puttemans2018comparing}, Puttemans et al. present a solution to detect coconut trees based on deep learning. Aparta et al. \cite{aparna2018cnn} apply convolutional neural networks to count coconut trees on plantations in India. Vargas-Muñoz et al. \cite{8899005} propose an active learning approach to detect coconut trees that seeks to reduce the effort of annotating images. The \cite{8899005} approach is divided into a stage of producing candidate patches for having a coconut tree and a stage where a CNN determines whether a patch has a coconut tree. We propose a different way to produce this classifier.

@@

  \end{tikzpicture}

  \end{center}
  \caption[An output example of the algorithm to compute a core stable coalition structure.]{An output example of the algorithm to compute a core stable coalition structure for games represented by forests. Each color represents a coalition.}
  \label{fig:tree}
\end{figure}

>>>>

Classification of tree species in aerial images has been actively investigated~\cite{fassnacht2016review}. In \cite{puttemans2018comparing, aparna2018cnn}, the authors present solutions to detect coconut trees based on convolutional neural network (CNN) models. Vargas-Muñoz et al.~\cite{8899005} propose an active learning approach to reduce human effort in annotating images of coconut trees. They divide the problem in two stages: a stage that produces candidate image patches and a stage in which a CNN identifies the candidate patches with a coconut tree. We propose a different way to produce this classifier.

@@

  \end{tikzpicture}
  \end{center}
  \label{fig:tree}
\end{figure}
